Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
adding "~" for \cite{}.
adding TBD placeholder.
adding references.

\item
    We improve CI support for Doctest and Hspec
    (Section~\ref{sec:TBD})

@@

\item[property]
    Property means a QuickCheck property as defined in
    \cite{quickcheck}.

@@

\begin{itemize}
\item
    For user documentation,
    Haddock does not have markup to describe evidence.
\item
    For code documentation,
    Hspec does not provide combinators to express expectations with
    BDD terminology.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Automatic discovery of specs}
\label{sec:solution-discovery}
We want to automatically discover all specs of a project, so that we
can run them all together.  This requires to automatically generate
boilerplate code, similar to what is shown in
Section~\ref{sec:problem-discovery}.

>>>>

\item
    We improve CI support for Doctest and Hspec
    (Section~\ref{sec:solution-discovery} and Section~\ref{sec:implementation-discovery})

@@

\item[property]
    Property means a QuickCheck property as defined in~\cite{quickcheck}.

@@

\begin{itemize}
\item
    For user documentation,
    Haddock does not have markup to describe evidence.
\item
    For code documentation,
    Hspec does not provide combinators to express expectations with
    BDD terminology.
\item TBD for CI
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Automatic discovery of specs}
\label{sec:solution-discovery}

We want to automatically discover all specs of a project, so that we
can run them all together.  This requires to automatically generate
boilerplate code, similar to what is shown in
Section~\ref{sec:problem-discovery}.
